Report - September 2017

### 2017-09-27 report.Rmd
removed old code from report.Rmd

---
title: "Report - September 2017"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")

@@

---
title: "Report - June 2017"
---

Note the forecast for D. spectabalis this month.

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
ds_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "newmoonnumber",
               obs_val_col_name = 'DS',
               for_data = for_data,
               for_date_col_name = "newmoonnumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(ds_forecast)

```

There is an increasing change that we will see a spectab in the coming months. Does this mean Stephanie will return?

>>>>

---
title: "Report - September 2017"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
library(portalr)

@@
